\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 coqimpl.tex
Resolve comments.

Upon \lsti{End}~\lsti{subst}, a module type named \lsti{STLC\_subst} is generated.
%
As discussed in \cref{sec:latebind}, \lsti{subst} can be further bound,\EDJ{If we don't allow further binding case handler(mentioned in your last reply), how do the user further bind the subst? I mean in the surface syntax}\YZreply{The position is that individual case handlers cannot be further bound, but the recursive function itself can be further bound by acquiring new case handlers.}
so its definition is not exposed to the fields that come after it.
Accordingly, the translation \lsti{STLC\_subst} merely declares the type of \lsti{subst}
and the existence of its propositional equalities, leaving \lsti{subst} undefined
and the equalities unproven.
%
The propositional equalities are stated in terms of the case handlers,
whose definitions \emph{are} available through the \lsti{self} parameter.
So Coq can simplify, for example, \lsti{subst_tm_unit_eq}'s type to
\lsti!\forall x t, self.subst self.tm_unit x t = self.tm_unit!.
The equalities will be included and available for use in the
translations of the subsequent fields through their \lsti{self}
parameters.

>>>>

Upon \lsti{End}~\lsti{subst}, a module type named \lsti{STLC\_subst} is generated.
%
As discussed in \cref{sec:latebind}, \lsti{subst} can be further bound,
% \EDJ{If we don't allow further binding case handler(mentioned in your last reply), how do the user further bind the subst? I mean in the surface syntax}\YZreply{The position is that individual case handlers cannot be further bound, but the recursive function itself can be further bound by acquiring new case handlers.}
so its definition is not exposed to the fields that come after it.
Accordingly, the translation \lsti{STLC\_subst} merely declares the type of \lsti{subst}
and the existence of its propositional equalities, leaving \lsti{subst} undefined
and the equalities unproven.
%
The propositional equalities are stated in terms of the case handlers,
whose definitions \emph{are} available through the \lsti{self} parameter.
So Coq can simplify, for example, \lsti{subst_tm_unit_eq}'s type to
\lsti!\forall x t, self.subst self.tm_unit x t = self.tm_unit!.
The equalities will be included and available for use in the
translations of the subsequent fields through their \lsti{self}
parameters.
